Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-26 TACAS2018/paper.tex

>>>>

Our abstraction refinement CEGIS loop is similar to CEGIS with solution generalization \cite{}.
However, it provides several improvements by exploiting modularity inside the loop.
The novelty of our approach relies on the synthesis refinement phase, which enables us
to generalise an existing candidate by means of optimisation. Rather than allow unsuitable
candidates reach the verification phase, and possibly require further induction on the synthesiser,
we use an optimizing algorithm which finds a local minima for the properties of interest. 
This reduces the chances of the optimised candidate failing verification. Furthermore, it allows
us to relax the quality of the synthesis, since unlikely candidates will still be optimised during this phase. 
Optimization may also enter its own refinement loop, since it is possible for the
counterexample to indicate which properties need optimizing (i.e. the ones that are failing).
